\begin{thebibliography}{MMM99}

\bibitem[Adam et Hendry]{Aglietta}
Adam C., et Hendry S., 
\textit{Le modèle vectoriel à correction d'erreur basé sur M1 : quelques extensions et applications},
Banque du Canada Working Paper, 2010.

\bibitem[Aglietta et Valla]{Aglietta}
Aglietta M. et Valla N., 
\textit{Macroéconomie financière}, 6e édition,
La Découverte, 2017.

\bibitem[Allen et McAleer]{Allen et McAleer}
Allen D. et McAleer M., 
\textit{A Nonlinear Autoregressive Distributed Lag (NARDL) Analysis of West Texas Intermediate Oil Prices and the DOW JONES Index}, Erasmus University Digital Repository,
2020.

\bibitem[Allen et al.]{Allen}
Allen F., Covi G., Gu X., Kowalewski O., Montagna M.,
\textit{The Interbank Market Puzzle}, 
2019.

\bibitem[Ang et Timmermann]{Ang et Timmermann}
Ang A. et Timmermann A., 
\textit{Regime Changes and Financial Markets}, Annual Review of Financial Economics, vol. 4, no. 1, pp. 313-337, 2012.

\bibitem[Arrata et al.]{Arrata}
Arrata W., Nguyen B., Rhamoun-Rousseau I. et Vari M.,
\textit{Eurosystem's asset purchases and money market rates}, 
Banque de France Working paper, 2017.

\bibitem[Balcilar et Ozdemir]{Balcilar et Ozdemir}
Balcilar M. et Ozdemir Z. A., 
\textit{Asymmetric and Nonlinear Adjustment in House Prices: Evidence from Threshold Autoregressive and Markov-Switching Models}, 
Economic Modelling, vol. 35, pp. 536-544, 2013.

\bibitem[Bech et Monnet]{Bech et Monnet}
Bech M., Monnet C., 
\textit{A search-based model of the interbank money market and monetary policy implementation}, No 529, BRI Working Paper, 2015.

\bibitem[Bech et Hobijn]{Bech et Hobijn}
Bech M. et Hobijn B.,
\textit{Technology Diffusion within Central Banking: The Case of Real-Time Gross Settlement},
International Journal of Central Banking, 2007.

\bibitem[Bennani et al.]{Clerc}
Bennani T., Clerc L., Coudert V., Dujardin M., Idier J.,
\textit{Politiques macroprudentielles},
Pearson, 2017.

\bibitem[Bianchi et Civelli]{Bianchi et Civelli}
Bianchi F. et Civelli A, 
\textit{Globalization and Inflation: Structural Evidence from a Time Varying VAR Approach}, 
Working Paper 13-20, Duke University, Department of Economics, 2013.

\bibitem[Bianchi]{Bianchi}
Bianchi F., 
\textit{The Great Depression and the Great Recession: A View from Financial Markets}, 
NBER Working Papers 21056, National Bureau of Economic Research, Inc., 2015.

\bibitem[Binder et Gross]{Binder et Gross}
Binder M. et Gross M., 
\textit{Regime Switching Global Vector AutoRegressive Model}, 
ECB Working Paper, n°1569, 2013.

\bibitem[Bismans et Damette]{Bismans}
Bismans F. et Damette O., 
\textit{Économétrie dynamique : modèles et applications}, 
Ellipses, 2023.

\bibitem[Bourbonnais et Terraza]{Terraza}
Bourbonnais R., Terraza M.,
\textit{Analyse des séries temporelles}, 3e édition,
Dunod, 2010.

\bibitem[Brunnermeier et Pedersen]{Brunnermeier et Pedersen}
Brunnermeier M. K. et Pedersen L. H., 
\textit{Market Liquidity and Funding Liquidity},
The Review of Financial Studies, vol. 22, no. 6, pp. 2201-2238, 2009.

\bibitem[Colletaz]{Colletaz}
Colletaz G.,
\textit{Introduction à la cointégration}, 2020.

\bibitem[Dameron]{Dameron}
Dameron P.,
\textit{Mathématiques des modèles dynamiques : analyse dynamique}, 
Economica, 2001.

\bibitem[Duca et Peltonen]{Duca et Peltonen}
Duca M. L. et Peltonen T. A.,
\textit{Assessing Systemic Risks and Predicting Systemic Events}, Journal of Banking \& Finance, vol. 37, no. 7, pp. 2183-2195, 2013.

\bibitem[Engle et Granger]{Engle et Granger}
Engle R. F. et Granger C. W. J., \textit{Co-integration and error correction: representation estimation and testing}, 
Econometrica, vol.55, n°2, mars 1987.

\bibitem[Engle et Yoo]{Engle et Yoo}
Engle R. F. et Yoo B. S., \textit{Forecasting and testing in co-integrated systems}, 
Journal of Econometrics, p.143-159, 1987.

\bibitem[Francq et Zakoian]{Francq et Zakoian}
Francq C., et Zakoian J-M.,
\textit{Modèles GARCH : structure, inférence statistique et applications financières},
Economica, 2009.

\bibitem[Gourieroux et Monfort]{Gourieroux et Monfort}
Gourieroux C. et Monfort A., 
\textit{Séries temporelles et modèles dynamiques},
2e édition, Economica, 1999.

\bibitem[Hamilton]{Hamilton} 
Hamilton, J. D.,
\textit{A New Approach to the Economic Analysis of Nonstationary Time Series and the Business Cycle}, Econometrica, vol. 57, no. 2, pp. 357-384, 1989.

\bibitem[Holló et al.]{Hollo} 
Holló D., Kremer M., et Lo Duca M., 
\textit{CISS - A Composite Indicator of Systemic Stress in the Financial System},
European Central Bank Working Paper Series, no. 1426, Mars, 2012.

\bibitem[Hubrich et Tetlow]{Hubrich et Tetlow}
Hubrich K. et Tetlow R., 
\textit{Financial Stress and Economic Dynamics : the Transmission of Crises},
ECB Working Paper, N°1728, 2O14.

\bibitem[Hurlin]{Hurlin}
Hurlin C., 
\textit{Modèle à retards distribués et modèles ARDL},
Université d'Orléans, Avril, 2O19.

\bibitem[Kole et Van Dijk]{Kole et Van Dijk}
Kole E. et Van Dijk D., 
\textit{Moments, Shocks and Spillovers in
Markov-Switching VAR Models},
Tinbergen Institute Discussion Paper, 2023.

\bibitem[Greene]{Greene}
Greene W.,
\textit{Économétrie},
5e édition,
Pearson, 2005.

\bibitem[Johansen et Juselius]{Johansen}
Johansen S. et Juselius K.,
\textit{ Maximum likelihood estimation and
inference on cointegration – with applications to the demand for money},
Oxford Bulletin of Economics and Statistics,
1990.

\bibitem[Kibala Kuma]{Kibala}
Kibala Kuma J., 
\textit{Modélisation ARDL, Test de cointégration aux bornes et Approche de Toda-Yamamoto: éléments de théorie et pratiques sur logiciels},
Licence, Congo-Kinshasa, 2018.

\bibitem[Kibala Kuma]{Kibala}
Kibala Kuma J., 
\textit{Cointégration et modèle à correction d'erreur : pratique sur Eviews},
Licence, Congo-Kinshasa, 2018.

\bibitem[Kibala Kuma]{Kibala}
Kibala Kuma J., 
\textit{Le modèle VAR structurel : élements de théorie et pratiques sur logiciel},
Licence, Congo-Kinshasa, 2018.

\bibitem[Krolzig]{Krolzig}
Krolzig H. M., 
\textit{Markov-Switching Vector Autoregressions: Modelling, Statistical Inference, and Application to Business Cycle Analysis},
Berlin: Springer-Verlag, 1997.

\bibitem[Ruch et Chabanol]{Ruch et Chabanol}
Ruch J.J. et Chabanol M.L., 
\textit{Chaînes de Markov},
Préparation à l'agrégation Bordeaux 1, 2013.

\bibitem[Mignon]{Mignon}
Mignon V.,
\textit{Économétrie : théorie et applications},
2e édition,
Economica, 2022.

\bibitem[Mills]{Mills}
Mills T.C.,
\textit{The Econometric Modelling of Financial Time Series},
2nd edition, Cambridge University Press.

\bibitem[Narayan]{Narayan}
Narayan P.K.,
\textit{Reformulating Critical Values for the Bounds F-Statistics
Approach to Cointegration : An Application to the Tourism Demand Model for Fiji}, 
Department of Economics, Discussion Papers, No.02/04, Monash University, 2004.

\bibitem[Perez et al.]{Perez}
Pérez S., Yasmina, Lozoya C., García Ramos L. et Arregui Gil J-M.,
\textit{Spread between the euro short-term rate (€STR) and the deposit facility rate}, Economic Bulletin - Banco de España, 2023.

\bibitem[Pesaran et Shin]{Pesaran et Shin}
Pesaran M.H., et Shin Y.,
\textit{An Autoregressive Distributed-Lag Modelling
Approach to Cointegration Analysis},
Econometrics and Economic Theory, p. 371-413, 1998.

\bibitem[Pesaran et al.]{Pesaran}
Pesaran M.H., Shin Y., Smith R.,
\textit{Bounds testing approaches to the analysis of level relationships},
Journal Applied of Econometrics, 2001.

\bibitem[Phillips Perron]{Phillips Perron}
Phillips, P. et Perron, P.,
\textit{ Time Series Regression with a Unit Root},
Econometrica, vol.55, No.2, Mars, pp. 277-301, 1987.

\bibitem[Phillips Perron]{Phillips Perron}
Phillips, P. et Perron, P.,
\textit{Testing for a Unit Root in Time Series Regression},
Biometrica, Vol.75, pp. 335-46, 1988.

\bibitem[Pinshi]{Pinshi}
Pinshi C., 
\textit{Repenser le modèle à correction d’erreurs dans l’analyse macroéconométrique}, 
Une revue. 2021

\bibitem[Schrimpf et Sushko]{Schrimpf et Sushko}
Schrimpf A., Sushko V.,
\textit{Après le LIBOR : une introduction aux nouveaux taux
de référence}, Rapport trimestriel BRI, 2019.

\bibitem[Schorderet]{Schorderet}
Schorderet Y., 
\textit{Asymmetric Cointegration},
University of Geneva, 2003

\bibitem[Shin et al.]{Shin}
Shin Y., Yu B., et Greenwood-Nimmo M.,
\textit{Modelling asymmetric cointegration and dynamic multipliers in a nonlinear ARDL framework}, 
The Festschrift in Honor of Peter Schmidt.: Econometric Methods and Applications, p. 281–314, 2014.

\bibitem[Vari]{Vari}
Vari M., 
\textit{Monetary policy transmission with interbank market fragmentation}, 
2016.

\newblock

\bibitem[BCE]{BCE}
Banque Centrale Européenne : \texttt{www.ecb.europa.eu}

\bibitem[BDF]{BDF}
Banque de France : \texttt{www.banque-france.fr}

\end{thebibliography}
